\documentclass[11pt,letterpaper]{article}

% ---------------------------------------------------------
% PACKAGES
% ---------------------------------------------------------
\usepackage[margin=1in]{geometry}
\usepackage{fontspec}
\usepackage{textcomp}
\setmainfont{EB Garamond}[
  Mapping=
]
\usepackage[hidelinks]{hyperref}
\usepackage{xurl}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{fancyhdr}
\usepackage{parskip}
\usepackage{tabularx}
\usepackage{booktabs}

% Professional Blue Theme
\definecolor{briefblue}{RGB}{0, 51, 102}

% Header/Footer
\pagestyle{fancy}
\fancyhf{}
\lhead{\footnotesize \textcolor{gray}{Interview Preparation: Security Controller at Palantir}}
\rhead{\footnotesize \textcolor{gray}{ Monday, February 16, 2026 }}
\cfoot{\thepage}
\renewcommand{\headrulewidth}{0.4pt}

% Section Styles
\titleformat{\section}{\Large\bfseries\color{briefblue}}{}{0pt}{}[\titlerule]
\titlespacing*{\section}{0pt}{12pt}{8pt}
\titleformat{\subsection}{\large\bfseries\color{briefblue}}{}{0pt}{}

% ---------------------------------------------------------
\begin{document}

% ---------------------------------------------------------
% COVER PAGE
% ---------------------------------------------------------
\begin{titlepage}
    \centering
    \vspace*{2cm}
    {\Huge \bfseries \textcolor{briefblue}{Interview Preparation Guide}}
    
    \vspace{1cm}
    {\huge Security Controller}
    
    \vspace{0.5cm}
    {\Large Palantir}
    
    \vfill
    \begin{flushleft}
        \textbf{Candidate:} Johnny Silverhand\\
        \textbf{Date:} Monday, February 16, 2026\\
        \textbf{Classification:} Confidential / For Internal Performance Coaching
    \end{flushleft}
\end{titlepage}

% ---------------------------------------------------------
\section*{1. Priority Talking Points (Force Multipliers)}


\subsection*{ End-to-End Cryptographic Custodianship }
\textbf{Context:} The JD's emphasis on managing the full lifecycle of cryptographic materials.
\begin{itemize}[leftmargin=0.2in, label=--]

  \item Discuss experience in the procurement, inventory control, and secure disposal of Type 1 cryptographic material during USMC and Militech-led missions.

  \item Emphasize 100\% accountability records for sensitive field comms assets in high-threat zones.

\end{itemize}

\subsection*{ Vetting \& Clearance Program Management }
\textbf{Context:} Managing the personnel clearance programme and secure facility access.
\begin{itemize}[leftmargin=0.2in, label=--]

  \item Reframe 'Tactical Team Leader' as a Personnel Security role responsible for the vetting and continuous evaluation of compartmented team members.

  \item Align current PMC-based vetting experience with UKG DV and compartmented clearance eligibility.

\end{itemize}

\subsection*{ Operational Facility Hardening }
\textbf{Context:} Leading the management and protection of classified materials and secure facilities.
\begin{itemize}[leftmargin=0.2in, label=--]

  \item Leverage OSINT on Palantir's European HQ to discuss physical security systems, SOP development, and incident response latency.

  \item Reference the 'adversary perspective' to identify physical-layer vulnerabilities in air-gapped mainframes.

\end{itemize}

\subsection*{ Inter-Agency Liaison (MoD/Intel) }
\textbf{Context:} Serving as the principal liaison with UK Intelligence and Defence partners.
\begin{itemize}[leftmargin=0.2in, label=--]

  \item Highlight successful strategic coordination with high-tier partners (Rogue, Blackhand) to align security objectives across competing interests.

  \item Commitment to the 'Western Superiority' mission logic and the ethical auditing of national security systems.

\end{itemize}

\subsection*{ Zero-Latency Incident Response }
\textbf{Context:} The 60-minute response time and after-hours/weekend on-call duties.
\begin{itemize}[leftmargin=0.2in, label=--]

  \item Proven ability to maintain mission readiness 24/7 in 'Always-On' tactical environments.

  \item Discuss managing high-intensity field extractions where response time was measured in seconds, not minutes.

\end{itemize}


% ---------------------------------------------------------
\section*{2. Anticipated Interview Questions}

\subsection*{Technical Questions}

\textbf{Q: How do you manage the procurement and distribution of cryptographic materials while maintaining 100\% policy compliance?} \\
\textbf{A:} I implement a strict provenance-tracking protocol that matches Palantir's own data lineage standards. My approach involves redundant auditing of procurement logs and real-time inventory tracking, ensuring that every sensitive asset is accounted for from arrival at the facility to its secure disposal. I view the physical asset as a unit of data that must remain encrypted through custody. 
\vspace{0.5em}

\textbf{Q: Explain your process for conducting a security briefing for personnel entering a compartmented facility.} \\
\textbf{A:} My briefings focus on 'The Human Perimeter.' I don't just read the SOP; I ensure personnel understand the specific threat vectors relevant to their mission. I emphasize the 'Least Privilege' principle and ensure that all staff are aware of their personal accountability in maintaining the facility's DV-cleared integrity. 
\vspace{0.5em}


\subsection*{Behavioral Questions (STAR Method)}

\textbf{Q: Give an example of a time you identified a flaw in a security process and corrected it.} \\
\textbf{A:} (STAR) Situation: During a Militech-backed extraction mission, I noticed a latency gap in our real-time cryptographic asset tracking. Task: Harden the tracking protocol without increasing operational friction. Action: I implemented a 'Dual-Key' field audit system that mirrored secure facility protocols. Result: Eliminated tracking drift and ensured 100\% material extraction during a high-fire rooftop extraction. 
\vspace{0.5em}

\textbf{Q: Describe a high-pressure situation where you had to liaise between multiple stakeholders with conflicting priorities.} \\
\textbf{A:} (STAR) Situation: Coordinating an assault on Arasaka Tower with multiple PMC and independent teams. Task: Align security and communications protocols across four distinct organizations. Action: I served as the central Security Command, establishing a unified cryptographic standard and a clear chain of command for incident response. Result: Successfully integrated intelligence requirements across the organization, achieving the objective with 0\% friendly-fire incidents. 
\vspace{0.5em}


\subsection*{Strategic Questions}

\textbf{Q: How would you handle a situation where a high-tier Palantir executive requested a bypass of a standard security protocol?} \\
\textbf{A:} I adhere to Alex Karp's philosophy of 'Accountability over Apathy.' In a high-clearance environment, there are no 'bypasses.' I would professionally deny the request based on the risk to the mission's UKG integrity and immediately document the event. A Security Controller's role is to be the systems' most rigorous auditor, regardless of rank. 
\vspace{0.5em}

\textbf{Q: What is the strategic value of maintaining a 60-minute response time for Palantir's UK mission?} \\
\textbf{A:} It is about 'Technical Latency.' Palantir's advantage is speed and decision-quality. If the physical security command has a latency of more than 60 minutes, it creates a window of opportunity for adversaries to compromise the very systems (Foundry/Gotham) that the MoD relies on. I ensure the physical perimeter is as fast as the digital one. 
\vspace{0.5em}


% ---------------------------------------------------------
\section*{3. Strategic Questions to Ask}

\begin{itemize}[leftmargin=0.2in, label=--]

  \item How does the Security Controller role interface with the Apollo CI/CD team when deploying software to air-gapped MoD environments?

  \item With the £750M MoD expansion, what are the current KPIs for scaling the personnel clearance programme without losing vetting depth?

  \item Can you describe the internal incident response hierarchy when a facility anomaly is detected after-hours?

  \item How does the London office balance the 'Forward Deployed' culture with the stringent physical security requirements of a UKG-cleared facility?

\end{itemize}

% ---------------------------------------------------------
\section*{4. Quick Reference Card}

\begin{table}[h]
\centering
\begin{tabularx}{\textwidth}{X X X}
\toprule
\textbf{Top 3 Strengths} & \textbf{Top 3 Gaps (Reframed)} & \textbf{Company Hooks} \\
\midrule

 Field-Hardened Cryptographic material handling (Type 1). & 
 Explicit UKNDS training (Ready for immediate certification). & 
 £750M MoD AI platform expansion (Strategic Growth). \\

 Expertise in High-Latency Liaison \& Tactical Coordination. & 
 UKG DV-Clearance (Eligible via high-stakes PMC Vetting history). & 
 Apollo Engine air-gapped deployments (Technical Challenge). \\

 Uncompromising dedication to Mission Integrity \& Ethical Auditing. & 
 Night City location (Relocation ready to within the 60-minute radius). & 
 Alex Karp's 'Patriotic Tech' philosophy (Cultural Match). \\

\bottomrule
\end{tabularx}
\end{table}

\end{document}