\documentclass[9pt]{article}

% ---------------------------------------------------------
% USER CONFIGURATION
% ---------------------------------------------------------
\newcommand{\myname}{Johnny Silverhand}
\newcommand{\myclearance}{Ex-Military (Deserter)}
\newcommand{\mylocation}{Night City}
\newcommand{\myphone}{N/A - Of{f}-Grid}
\newcommand{\myemail}{burnitdown@samurai.nc}
\newcommand{\mylinkedin}{N/A - Anti-Corporate}

% ---------------------------------------------------------
% FONT & FORMATTING
% ---------------------------------------------------------

\usepackage[margin=0.5in]{geometry}
\usepackage{ebgaramond}

\usepackage{enumitem}
\setlist{itemsep=0pt, parsep=0pt, topsep=0pt, partopsep=0pt}

\usepackage{multicol}
\usepackage[hidelinks]{hyperref}
\usepackage{parskip}
\usepackage{sectsty}
\sectionfont{\centering}

\usepackage{setspace}
\singlespacing
 
\setlength{\parindent}{0pt}
\setstretch{1.05}

% Bullet formatting
\setlist[itemize]{leftmargin=0.3in, itemsep=2pt}

\usepackage{titlesec}

% Section formatting
\titleformat*{\section}{\centering\large\bfseries}
\titlespacing*{\section}{0pt}{6pt}{3pt}

% ---------------------------------------------------------
% CUSTOM ENVIRONMENTS / COMMANDS
% ---------------------------------------------------------

% Consistent list environment for resume bullets
\newenvironment{resumeItemList}{%
  \begin{itemize}[leftmargin=0.25in, itemsep=2pt, topsep=2pt]
}{%
  \end{itemize}
}

% Handy macro for role header lines:
\newcommand{\role}[5]{%
  \textbf{#1} -- #2 \quad\textbar\quad \textit{\textbf{#3}} \quad\textbar\quad #4 -- #5%
}

% ---------------------------------------------------------
\begin{document}

% ---------------------------------------------------------
% HEADER
% ---------------------------------------------------------
\begin{center}
    {\Large \textbf{\myname}}\\[4pt]
    \myclearance \quad\textbar\quad \mylocation \\
    \myphone \quad\textbar\quad \href{mailto:\myemail}{\myemail} \quad\textbar\quad \href{https://\mylinkedin}{\mylinkedin}
\end{center}

\vspace{0.5em}
\hrule
\vspace{0.75em}

% ---------------------------------------------------------
\section*{PROFESSIONAL SUMMARY}

Iconic Rockerboy, SAMURAI frontman, and anti-corporate revolutionary. Combat veteran of the Second Central American War (Nicaragua) with extensive experience in tactical sabotage, adversary emulation, and mass-market psychological operations. Known for high-impact social engineering through chrome-rock and orchestrating the 2023 Arasaka Tower 'Night City Holocaust'. Dedicated to dismantling corporate hegemony and exposing the 'Soulkiller' program. Note: Some historical accounts may vary due to engram memory unreliability.

% ---------------------------------------------------------

\section*{SKILLS}

\setlength{\columnsep}{1em}
\begin{multicols}{3}
\begin{itemize}[leftmargin=*, rightmargin=0pt, itemsep=0pt, parsep=0pt, topsep=0pt, partopsep=0pt]
\small

  \item Charismatic Leadership (+10)

  \item Tactical Sabotage \& Demolitions

  \item Lead Guitar \& Songwriting (+10)

  \item Combat Prof{i}ciency (Malorian 3516 / CQC)

  \item Cybernetic Integration \& Interface Plugs

  \item Hacking \& Cyberdeck Operations

\end{itemize}
\end{multicols}


% ---------------------------------------------------------
\section*{PROFESSIONAL EXPERIENCE}


\role{Militech (Militech-led Raid on Arasaka Tower)}{Night City}{Tactical Team Leader}{Aug 2023}{Aug 2023}

\begin{resumeItemList}

  \item {Co-led a Militech-backed assault on Arasaka Tower to deliver a 5-kiloton tactical nuke, ef{f}ectively ending the Fourth Corporate War.}

  \item {Coordinated with Morgan Blackhand and Rogue Amendiares for high-stakes urban inf{i}ltration and rooftop extraction.}

  \item {Executed search and rescue mission for Alt Cunningham's consciousness within the Arasaka mainframe under intense combat conditions.}

\end{resumeItemList}
\vspace{0.5em}

\role{SAMURAI}{Night City}{Frontman \& Lead Guitar}{2003}{2008}

\begin{resumeItemList}

  \item {Co-founded the legendary chrome-rock band SAMURAI, achieving international fame and platinum record status.}

  \item {Composed and performed 'Chippin' In', 'Never Fade Away', and 'A Like Supreme' - anthems of the anti-establishment movement.}

  \item {Utilized global tours to broadcast anti-corporate messages and shift public perception of veterans disillusioned by war.}

\end{resumeItemList}
\vspace{0.5em}

\role{U.S. Marine Corps (2nd Marine Division)}{Nicaragua}{Infantryman}{2003}{2003}

\begin{resumeItemList}

  \item {Deployed to the Second Central American War, participating in high-intensity jungle warfare and tactical raids.}

  \item {Lost left arm in combat; successfully integrated a silver prosthetic, establishing the 'Silverhand' operational identity.}

  \item {Exposed government corruption in the 2009 solo album 'SINS of Your Brothers' after deserting service.}

\end{resumeItemList}
\vspace{0.5em}


% ---------------------------------------------------------
\section*{EDUCATION}

\begin{center}

\textbf{Tactical Survival \& Combat Training} \quad\textbar\quad Streets of Night City / Nomad Clans \quad\textbar\quad 1988--2003 \\
\textit{Focus: Small Arms, Survivalism, and Music Theory}\\

\end{center}

% ---------------------------------------------------------


% ---------------------------------------------------------
\section*{CERTIFICATIONS}

\begin{multicols}{2}
\centering
\small

DCRT (DoD Certif{i}ed Red Team) --- Equivalent\\

SAMURAI Platinum Record (Multi-year)\\

\end{multicols}

% ---------------------------------------------------------

\section*{TECHNICAL SKILLS}

\begin{center}
\small
\textbf{Of{f}ensive Operations} \quad\textbar\quad Tactical Sabotage • System Inf{i}ltration • Demolitions • Red Teaming\\
\textbf{Cyberware} \quad\textbar\quad Chromed Left Arm • Sandevistan Boost • Cyberoptics • Interface Plugs\\
\textbf{Artistic} \quad\textbar\quad Lead Guitar • Composition (+10) • Mass Inf{l}uence\\

\end{center}


% ---------------------------------------------------------

\section*{AWARDS \& RECOGNITION}

\begin{center}
\small
Night City Legend (Posthumous)\\
Breathtaking Achievement (Apparel Collection)\\
Ghost Story Status (Arasaka Corporation internal lore)\\

\end{center}


\end{document}