\documentclass[11pt]{article}

% ---------------------------------------------------------
% PACKAGES & THEME
% ---------------------------------------------------------
\usepackage[margin=1in]{geometry}
\usepackage{fontspec}
\usepackage{textcomp}
\setmainfont{EB Garamond}[
  Mapping=
]
\usepackage[hidelinks]{hyperref}
\usepackage{parskip}
\usepackage{xcolor}

\definecolor{briefblue}{RGB}{0, 51, 102}

% ---------------------------------------------------------
\begin{document}

% --- SENDER INFO ---
\begin{flushright}
    \textbf{Johnny Silverhand}\\
    London, UK (Relocation Ready)\\
    N/A - Off-Grid\\
    burnitdown@samurai.nc\\
    \href{https://linkedin.com/in/johnnysilverhand}{linkedin.com/in/johnnysilverhand}
\end{flushright}

\vspace{1em}

% --- DATE ---
\today

\vspace{1em}

% --- RECIPIENT INFO ---
\textbf{Hiring Team}\\
Palantir\\
London, UK

\vspace{2em}

% --- SALUTATION ---
Dear Hiring Manager,

\vspace{1em}

% --- BODY ---
Palantir's establishment of its European Defence Headquarters in London represents a significant escalation in the UK's ability to maintain a decisive technical advantage over sophisticated state adversaries. However, the integrity of these missions depends entirely on the Security Controllers who manage the facilities and personnel vetting behind the scenes. I am writing to apply for the Security Controller position, bringing a combat-hardened background in managing secure facilities and highly classified cryptographic materials under the most intense operational friction.

My tenure as a Tactical Team Leader and my service in the U.S. Marine Corps provided me with a granular understanding of the 'physical-to-digital' security bridge. I have directed missions requiring 100% security of sensitive field communications and cryptographic Type 1 material during high-intensity tactical raids. This experience as a Compartmented Security Officer (CSO) ensures that I am prepared to manage Palantir's UKG-cleared facilities with zero latency, ensuring that your cryptographic assets and personnel clearance programs remain air-tight and audit-ready.

I am particularly drawn to Palantir's mission because it rejects the 'shallow' security models of commercial tech in favor of active, high-integrity defense. My history in unconventional warfare has instilled a proactive 'adversary logic'—the ability to identify and neutralize perimeters vulnerabilities from the perspective of the attacker. I thrive in 'always-on' environments requiring a 60-minute response time, and I am prepared to apply my technical depth and leadership to support your most sensitive UK Intelligence and Defence deployments.

I am eager to discuss how my unique background in compartmented security and tactical leadership can serve as a force multiplier for Palantir's UK Security Command. I look forward to the opportunity for a briefing on your current security requirements and how I can support the resilience of your London-based operations. Thank you for your time and consideration.

\vspace{2em}

% --- CLOSING ---
Sincerely,

\vspace{3em}

Johnny Silverhand

\end{document}