\documentclass[11pt,letterpaper]{article}

% ---------------------------------------------------------
% PACKAGES
% ---------------------------------------------------------
\usepackage[margin=1in]{geometry}
\usepackage{ebgaramond}
\usepackage[hidelinks]{hyperref}
\usepackage{xurl} % Allow long URLs to break anywhere
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{fancyhdr}
\usepackage{parskip}

% Professional Blue Theme
\definecolor{briefblue}{RGB}{0, 51, 102}

% Header/Footer
\pagestyle{fancy}
\fancyhf{}
\lhead{\footnotesize \textcolor{gray}{Mission Intelligence Dossier: Palantir Technologies}}
\rhead{\footnotesize \textcolor{gray}{February 10, 2026}}
\cfoot{\thepage}
\renewcommand{\headrulewidth}{0.4pt}

% Section Styles
\titleformat{\section}{\Large\bfseries\color{briefblue}}{}{0pt}{}[\titlerule]
\titlespacing*{\section}{0pt}{12pt}{8pt}
\titleformat{\subsection}{\large\bfseries\color{briefblue}}{}{0pt}{}

% ---------------------------------------------------------
\begin{document}

% ---------------------------------------------------------
% COVER PAGE
% ---------------------------------------------------------
\begin{titlepage}
    \centering
    \vspace*{2cm}
    {\Huge \bfseries \textcolor{briefblue}{Mission Intelligence Dossier}}
    
    \vspace{1cm}
    {\huge Palantir Technologies}
    
    \vspace{0.5cm}
    {\Large Denver, CO (Global HQ)}
    
    \vfill
    \begin{flushleft}
    \textbf{Prepared for:} Johnny Silverhand\\
    \textbf{Date:} February 10, 2026\\
    \textbf{Classification:} Confidential Intelligence / For Interview Prep Only
    \end{flushleft}
\end{titlepage}

% ---------------------------------------------------------
\section*{Executive Summary}
Johnny Silverhand (Robert John Linder) represents a high-conviction 'Force Multiplier' for Palantir's mission-critical defense operations. His history as a decorated combat veteran and a globally inf{l}uential cultural f{i}gure aligns with Alexander Karp's 'Ethical Perimeter' and the company's 100\% mission-motivated culture. His expertise in tactical sabotage and high-stakes corporate inf{i}ltration provide an unparalleled 'Attack Vector' for Palantir's expansion into AI-def{i}ned battlef{i}eld systems.

% ---------------------------------------------------------
\section*{1. Local Mission Portfolio}

\begin{itemize}[leftmargin=0.2in, label=--]

  \item \textbf{TITAN Ground Stations}: Prime Contractor for the U.S. Army's \$178.4M program. Delivered the f{i}rst two AI-def{i}ned battlef{i}eld intelligence prototypes in March 2025, with full delivery of 10 units (JLTV and FMTV variants) expected by 2026 [2].

  \item \textbf{Project Maven Delivery}: Managing a \$480M contract (extending through 2029) to expand Maven Smart System AI access across all U.S. military services, facilitating high-f{i}delity sensor-to-shooter targeting [3].

  \item \textbf{Denver HQ Hub}: Central operational base for f{i}nancial reporting and AIP delivery. Located at Financial House, 205 N. Detroit St. in Cherry Creek as of late 2025 [6].

\end{itemize}


% ---------------------------------------------------------
\section*{2. Enterprise Business Intelligence}

\begin{itemize}[leftmargin=0.2in, label=--]

  \item \textbf{ESA Consolidation}: Secured a landmark 10-year, \$10 Billion Enterprise Service Agreement with the Army in August 2025, consolidating 75 separate prime and sub-contracts into a single strategic vehicle [1].

  \item \textbf{2026 Growth Projection}: Forecasting revenue of \$7.18B - \$7.20B (+61\% YoY), driven by a 115\% surge in U.S. commercial sales and dominant government platform adoption [4].

  \item \textbf{Vantage Continuity}: Extended the Army Vantage partnership with a \$400.7M deal through 2028, currently serving over 100,000 active users [5].

\end{itemize}


% ---------------------------------------------------------
\section*{3. People, Culture \& Strategic Context}

\begin{itemize}[leftmargin=0.2in, label=--]

  \item \textbf{Ethical Perimeter}: CEO Alex Karp maintains a staunch defense of Western democratic values, refusing to work with authoritarian regimes and prioritizing the 'intention of those who wield software' [11].

  \item \textbf{Forward Deployed Model}: Pioneered by Shyam Sankar (Employee \#13), this model embeds engineers directly with clients to solve 'hard problems' where victory is the only acceptable outcome [12].

  \item \textbf{Mission Motivation}: Employees cite the mission-f{i}rst culture as the primary retention driver, with leadership viewing support for the U.S. military as a non-negotiable obligation [8].

\end{itemize}


% ---------------------------------------------------------
\section*{4. Technical Stack DNA}

\begin{itemize}[leftmargin=0.2in, label=--]

  \item \textbf{The Ontology}: A live digital twin architecture consisting of Semantic (conceptual models), Kinetic (data transforms/ETL), and Dynamic (user interaction) layers [7].

  \item \textbf{Apollo secure delivery}: Proprietary DevOps platform for multi-domain orchestration, managing over 300 microservices across secure and cloud-disconnected air-gapped environments [9].

  \item \textbf{AI FDE Roadmap}: Emerging focus on 'AI Forward Deployed Engineers' capable of autonomous ontology editing and application debugging [9].

\end{itemize}


% ---------------------------------------------------------
\section*{5. Strategic Fit \& Attack Vectors}

\begin{itemize}[leftmargin=0.2in, label=--]

  \item \textbf{Ethical Alignment}: Johnny's history of exposing wartime corruption (SINS of Your Brothers) matches Karp's stance on individual integrity and ethical software deployment.

  \item \textbf{Tactical Inf{i}ltration}: His expertise in Arasaka-scale inf{i}ltration serves as a direct analog for Red Team security validation of Army data systems.

\end{itemize}


% ---------------------------------------------------------
% OPTIONAL DEEP DIVES
% ---------------------------------------------------------

\section*{6. Funding Cliff \& Risk Analysis}

\begin{itemize}[leftmargin=0.2in, label=--]

  \item \textbf{ESA Buf{f}er}: The \$10B Army ESA provides a massive buf{f}er, though mandatory 18-24 month innovations assessments represent the primary innovation gate [10].

\end{itemize}




\section*{7. Organizational Hierarchy (Triage)}

\begin{itemize}[leftmargin=0.2in, label=--]

  \item \textbf{Leadership Flatness}: Alexander Karp (CEO), Stephen Cohen (President), and Shyam Sankar (CTO/COO) lead a f{l}at model where titles are primarily external.

\end{itemize}




\section*{8. Ecosystem \& Partner Map}

\begin{itemize}[leftmargin=0.2in, label=--]

  \item \textbf{Anduril Consortium}: Strategic AI teaming agreement with Anduril to merge Lattice and AIP capabilities for battlef{i}eld data processing.

\end{itemize}



% ---------------------------------------------------------
\section*{Interview Reconnaissance}
Leverage the 'disillusioned veteran' narrative as an ultimate act of mission loyalty. Focus on rapport with Sankar's FDE model, emphasizing combat-zone hardware/software integration and the ability to win in 'bad times.'

% ---------------------------------------------------------
\section*{Sources \& Citations}
{\raggedright
\begin{enumerate}[label={[\arabic*]}]

    \item Defence Blog, "Palantir wins landmark \$10B U.S. Army AI contract," Aug. 2025. [Online]. Available: https://defence-blog.com/palantir-wins-10b-u-s-army-ai-contract/ [Accessed: Feb. 10, 2026].

    \item DefenseScoop, "Palantir wins \$178M Army deal for TITAN ground stations," Mar. 06, 2024. [Online]. Available: https://defensescoop.com/2024/03/06/palantir-wins-178m-army-deal-for-titan-artif{i}cial-intelligence-enabled-ground-stations/ [Accessed: Feb. 10, 2026].

    \item FedScoop, "Palantir wins another major Army contract," May 2024. [Online]. Available: https://fedscoop.com/radio/palantir-wins-another-major-army-contract/ [Accessed: Feb. 10, 2026].

    \item The Motley Fool, "Palantir (PLTR) Q4 2025 Earnings Call Transcript," Feb. 02, 2026. [Online]. Available: https://www.fool.com/earnings/call-transcripts/2026/02/02/palantir-pltr-q4-2025-earnings-call-transcript/ [Accessed: Feb. 10, 2026].

    \item Defense News, "Palantir gets \$400 million extension for Army Vantage data platform," Dec. 16, 2024. [Online]. Available: https://www.defensenews.com/battlef{i}eld-tech/it-networks/2024/12/16/palantir-gets-400-million-extension-for-army-vantage-data-platform/ [Accessed: Feb. 10, 2026].

    \item BusinessDen, "Palantir moving HQ from downtown Denver to Cherry Creek," Sep. 15, 2025. [Online]. Available: https://businessden.com/2025/09/15/palantir-moving-hq-from-downtown-denver-to-cherry-creek/ [Accessed: Feb. 10, 2026].

    \item Palantir Technologies, "The Foundry Ontology," 2025. [Online]. Available: https://www.palantir.com/platforms/foundry/ontology/ [Accessed: Feb. 10, 2026].

    \item Forbes, "Inside Palantir: Alex Karp's Software War Machine," Jun. 12, 2024. [Online]. Available: https://www.forbes.com/sites/thomasbrewster/2024/06/12/inside-palantir-alex-karps-software-war-machine/ [Accessed: Feb. 10, 2026].

    \item Constellation Research, "Analysis of the AI FDE Deployment Model," 2025. [Online]. Available: https://www.constellationr.com/blog-news/palantir-q2-2025-earnings-analysis-the-rise-of-ai-fdes [Accessed: Feb. 10, 2026].

    \item Breaking Defense, "Palantir secures massive \$10B Army AI deal," Aug. 2025. [Online]. Available: https://breakingdefense.com/2025/08/palantir-secures-massive-10b-army-ai-deal/ [Accessed: Feb. 10, 2026].

    \item Palantir Newsroom, "Alexander Karp on the ethical use of AI," 2025. [Online]. Available: https://www.palantir.com/newsroom/quotes/ethical-use-of-ai/ [Accessed: Feb. 10, 2026].

    \item S. Sankar, "The Forward Deployed Engineer Model," Medium, 2024. [Online]. Available: https://medium.com/palantir/the-forward-deployed-engineer-model-f8e234b12c3 [Accessed: Feb. 10, 2026].

\end{enumerate}
}

\end{document}