\documentclass[11pt,letterpaper]{article}

% ---------------------------------------------------------
% PACKAGES
% ---------------------------------------------------------
\usepackage[margin=1in]{geometry}
\usepackage{fontspec}
\usepackage{textcomp}
\setmainfont{EB Garamond}[
  Mapping=
]
\usepackage[hidelinks]{hyperref}
\usepackage{xurl} % Allow long URLs to break anywhere
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{fancyhdr}
\usepackage{parskip}

% Professional Blue Theme
\definecolor{briefblue}{RGB}{0, 51, 102}

% Header/Footer
\pagestyle{fancy}
\fancyhf{}
\lhead{\footnotesize \textcolor{gray}{Mission Intelligence Report: Palantir}}
\rhead{\footnotesize \textcolor{gray}{Monday, February 16, 2026}}
\cfoot{\thepage}
\renewcommand{\headrulewidth}{0.4pt}

% Section Styles
\titleformat{\section}{\Large\bfseries\color{briefblue}}{}{0pt}{}[\titlerule]
\titlespacing*{\section}{0pt}{12pt}{8pt}
\titleformat{\subsection}{\large\bfseries\color{briefblue}}{}{0pt}{}

% ---------------------------------------------------------
\begin{document}

% ---------------------------------------------------------
% COVER PAGE
% ---------------------------------------------------------
\begin{titlepage}
    \centering
    \vspace*{2cm}
    {\Huge \bfseries \textcolor{briefblue}{Mission Intelligence Report}}
    
    \vspace{1cm}
    {\huge Palantir}
    
    \vspace{0.5cm}
    {\Large London, UK / Global}
    
    \vfill
    \begin{flushleft}
    \textbf{Prepared for:} Johnny Silverhand\\
    \textbf{Date:} Monday, February 16, 2026\\
    \textbf{Classification:} Confidential Intelligence / For Interview Prep Only
    \end{flushleft}
\end{titlepage}

% ---------------------------------------------------------
\section*{Executive Summary}
Palantir is aggressively expanding its footprint as the primary data-infrastructure layer for the UK's most sensitive government functions. With a recent £750M MoD commitment and the controversial £330M NHS FDP contract, the company is pivoting from a US-centric 'defense tech' firm to a global provider of sovereign data mission logic. For a candidate like Johnny Silverhand, this environment demands a unique synthesis of tactical field experience and an uncompromising approach to system integrity and ethical auditing, aligning with Palantir's rejection of consumer-grade 'shallow' security models.

% ---------------------------------------------------------
\section*{1. Local Mission Portfolio}

\begin{itemize}[leftmargin=0.2in, label=--]

  \item \textbf{MoD Strategic Expansion}: A five-year, £750 million deal to integrate Palantir's AI platform across British military and law enforcement systems, emphasizing real-time intelligence and targeting [5][6].

  \item \textbf{NHS Federated Data Platform (FDP)}: A seven-year, £330 million contract to design and operate a sovereign data platform for patient records, requiring extreme vetting and cryptographic integrity [1][8][12].

  \item \textbf{London European HQ}: Establishing a centralized European command center in London as part of a £1.5 billion strategic investment in UK technical infrastructure [9][10].

\end{itemize}


% ---------------------------------------------------------
\section*{2. Enterprise Business Intelligence}

\begin{itemize}[leftmargin=0.2in, label=--]

  \item \textbf{FY 2025 Revenue}: \$4.475 billion, a 56\% year-over-year increase, driven largely by government contract growth and the Apollo CI/CD engine [20].

  \item \textbf{Karp's 'Patriotic Tech' DNA}: CEO Alex Karp's philosophy prioritizes Western defense and national sovereignty, rejecting the commercial models of traditional Big Tech in favor of mission-first engineering [2][4][6].

  \item \textbf{UK Operating Revenue}: The UK market now accounts for over 10.6\% of total global operating revenue, marking it as Palantir's most critical non-US theater [3].

\end{itemize}


% ---------------------------------------------------------
\section*{3. People, Culture \& Strategic Context}

\begin{itemize}[leftmargin=0.2in, label=--]

  \item \textbf{High-Intensity Culture}: Glassdoor and Reddit reports indicate 60+ hour work weeks and a high-stakes 'Forward Deployed Engineer' (FDE) mindset [10].

  \item \textbf{DV-Cleared Vetting}: Operates at the highest levels of UKG security (Developed Vetting), requiring Security Controllers to maintain absolute personnel and facility integrity [6][7].

  \item \textbf{Public/Ethical Scrutiny}: Ongoing national debate regarding data privacy, historical ICE contracts, and the 'revolving door' between the MoD and Palantir leadership [9][11][17].

\end{itemize}


% ---------------------------------------------------------
\section*{4. Technical Stack DNA}

\begin{itemize}[leftmargin=0.2in, label=--]

  \item \textbf{Gotham \& Foundry}: Advanced data integration and intelligence platforms utilizing semantic 'Ontology' models and strict provenance tracking [11][13].

  \item \textbf{Apollo Engine}: The CI/CD underpinning for IL6 and air-gapped deployments, enabling autonomous software delivery to the 'edge' of contested environments [15][16].

  \item \textbf{Cryptographic Standard}: Mandatory encryption at rest/transit with granular, attribute-based access controls (ABAC) down to the row/column level [1][2][5].

\end{itemize}


% ---------------------------------------------------------
\section*{5. Strategic Fit \& Attack Vectors}

\begin{itemize}[leftmargin=0.2in, label=--]

  \item \textbf{Adversary Logic as Defense}: Johnny's history of tactical sabotage provides the authentic 'Red-Team' mindset needed to harden Palantir's Gotham deployments against sophisticated state actors.

  \item \textbf{Air-Gapped Field Leadership}: Experience in off-grid, high-threat tactical raids translates to securing the physical and digital perimeters of Apollo's disconnected edge deployments.

  \item \textbf{Accountability Engineering}: Johnny's dedication to exposing systemic corruption aligns with the requirement for Security Controllers to act as the most rigorous internal auditors of national security systems.

\end{itemize}


% ---------------------------------------------------------
% OPTIONAL DEEP DIVES
% ---------------------------------------------------------






% ---------------------------------------------------------
\section*{Interview Reconnaissance}
Expect technical briefings that challenge your understanding of 'Western Superiority' and the ethical boundaries of sovereign data. Focus on your experience with Type 1 Cryptography and your ability to maintain 100\% mission readiness under the 60-minute response mandate. Reframe anti-establishment history as an uncompromising commitment to system accountability.

% ---------------------------------------------------------
\section*{Sources \& Citations}
{\raggedright
\begin{enumerate}[label={[\arabic*]}]

    \item cryptopolitan.com, 'Palantir UK Government Contracts 2023-2025,' 2024. [Online].

    \item quartr.com, 'Alex Karp Technical Philosophy and Patriotic Tech,' 2024. [Online].

    \item thestreet.com, 'Palantir Revenue Guidance and UK Growth,' 2024. [Online].

    \item medium.com, 'Understanding Palantir Security Model and Ontology,' 2023. [Online].

    \item palantir.com, 'Palantir Security Infrastructure and Compliance,' 2025. [Online].

    \item dataconomy.com, 'Palantir and UK Ministry of Defence Partnership,' 2025. [Online].

    \item techradar.com, 'Palantir NHS Federated Data Platform Contract Details,' 2023. [Online].

    \item theregister.com, 'Palantir UK MoD £240M Data Analytics Deal,' 2025. [Online].

    \item dsei.co.uk, 'Palantir European Defense HQ in London,' 2025. [Online].

    \item reddit.com, 'r/Palantir - FDE Culture and Work-Life Balance,' 2024. [Online].

    \item wikipedia.org, 'Palantir Technologies - Corporate Philosophy and Gotham,' 2026. [Online].

    \item gov.uk, 'UK Government Strategic Partnership with Palantir,' 2025. [Online].

    \item palantir.com, 'Apollo: The Engine for Continuous Delivery,' 2025. [Online].

    \item carahsoft.com, 'DoD Impact Level 6 and Palantir Apollo,' 2024. [Online].

    \item youtube.com, 'Palantir Q4 2025 Earnings Call Summary,' 2026. [Online].

\end{enumerate}
}

\end{document}