\documentclass[11pt,letterpaper]{article}

% ---------------------------------------------------------
% PACKAGES
% ---------------------------------------------------------
\usepackage[margin=1in]{geometry}
\usepackage{fontspec}
\usepackage{textcomp}
\setmainfont{EB Garamond}[
  Mapping=
]
\usepackage[hidelinks]{hyperref}
\usepackage{xurl}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{fancyhdr}
\usepackage{parskip}
\usepackage{tabularx}
\usepackage{booktabs}

% Professional Blue Theme
\definecolor{briefblue}{RGB}{0, 51, 102}
\definecolor{matchgreen}{RGB}{34, 139, 34}
\definecolor{gapred}{RGB}{178, 34, 34}

% Header/Footer
\pagestyle{fancy}
\fancyhf{}
\lhead{\footnotesize \textcolor{gray}{Opportunity Evaluation: Security Controller}}
\rhead{\footnotesize \textcolor{gray}{ Monday, February 16, 2026 }}
\cfoot{\thepage}
\renewcommand{\headrulewidth}{0.4pt}

% Section Styles
\titleformat{\section}{\Large\bfseries\color{briefblue}}{}{0pt}{}[\titlerule]
\titlespacing*{\section}{0pt}{12pt}{8pt}
\titleformat{\subsection}{\large\bfseries\color{briefblue}}{}{0pt}{}

% ---------------------------------------------------------
\begin{document}

% ---------------------------------------------------------
% COVER PAGE
% ---------------------------------------------------------
\begin{titlepage}
    \centering
    \vspace*{2cm}
    {\Huge \bfseries \textcolor{briefblue}{Opportunity Evaluation Report}}
    
    \vspace{1cm}
    {\huge Security Controller}
    
    \vspace{0.5cm}
    {\Large Palantir}
    
    \vfill
    \begin{center}
        \large \textbf{Match Score: 15.3\%} \\
        \textcolor{matchgreen}{\Huge \textbf{ NO-GO }}
    \end{center}
    
    \vfill
    \begin{flushleft}
    \textbf{Candidate:} Johnny Silverhand\\
    \textbf{Date:} Monday, February 16, 2026\\
    \textbf{Classification:} Internal / Candidate Strategy Portfolio
    \end{flushleft}
\end{titlepage}

% ---------------------------------------------------------
\section*{Executive Summary}
The candidate remains a NO-GO for the UKG-specific Security Controller role due to the terminal citizenship and clearance requirements. However, the 'Strategic Bridging' performed during tailoring reveals an exceptional fit for Palantir's high-tier private security, offensive research, or international defense deployments where field-hardened leadership and 'Adversary Logic' are more valuable than specific government vetting. Recommend pivoting the application to Palantir's 'Global Security' or 'FDE' divisions.

% ---------------------------------------------------------
\section*{1. Weighted Scoring Matrix}

\begin{table}[h]
\centering
\begin{tabularx}{\textwidth}{l c c c X}
\toprule
\textbf{Category} & \textbf{Weight} & \textbf{Score} & \textbf{Weighted} & \textbf{Rationale} \\
\midrule
Required Skills & 40\% & 15\% & 6.0 \% & Possesses deep experience in Type 1 Cryptography and high-stakes vetting, but lacks UK citizenship/DV-clearance and UKNDS certifications. \\
Experience Level & 25\% & 20\% & 5.0 \% & Combat-proven tactical leadership is exceptional; however, compliance-based security auditing is 'bridged' rather than direct. \\
Nice-to-Have & 20\% & 10\% & 2.0 \% & Strong inter-agency liaison potential demonstrated through PMC strategic coordination roles. \\
Industry Match & 15\% & 15\% & 2.2 \% & Military veteran background aligns with Palantir's 'Patriotic Tech' DNA, despite previous anti-corporate history. \\
\midrule
\textbf{TOTAL} & \textbf{100\%} & - & \textbf{ 15.3\% } & \textbf{Final Fit Score} \\
\bottomrule
\end{tabularx}
\end{table}

% ---------------------------------------------------------
\section*{2. Critical Strengths}

\begin{itemize}[leftmargin=0.2in, label=--]

  \item Type 1 Cryptographic Custodianship -- Ensures 100\% accountability of sensitive digital assets in high-threat environments.

  \item Adversary Logic Integration -- Provides an authentic Red-Team perspective for hardening secure facilities against sophisticated breaches.

  \item Zero-Latency Decision Making -- Combat-hardened leadership capable of operating within the 60-minute response mandate.

\end{itemize}

% ---------------------------------------------------------
\section*{3. Gap Analysis \& Mitigation}


\subsection*{ UK Government Clearance (DV) }
\textbf{Status:} \textcolor{gapred}{ Terminal Block. Ineligibility for UK DV-clearance prevents access to compartmented intelligence. }. \\
\textbf{Mitigation:} Strategic Bridging: Reframe as 'Eligible for Private Sector Equivalent' and target Palantir's commercial or non-UKG defense portfolios.

\subsection*{ UKG Compliance Standards }
\textbf{Status:} \textcolor{gapred}{ Critical Gap. No formal experience with UK MoD or UK Intelligence security frameworks. }. \\
\textbf{Mitigation:} Highlight USMC and Militech security protocols as topological equivalents to UKG standards.


% ---------------------------------------------------------
\section*{4. Red Flag Verification}

\begin{itemize}[leftmargin=0.2in, label=--]
  \item \textbf{Certification Gap}: FLAG: Lacks UKNDS Crypto Custodian and CSO certifications.
  \item \textbf{Experience Gap}: CLEAR: Bridged via high-stakes facility security roles in the PMC sector.
  \item \textbf{Tech Stack Mismatch}: CLEAR: Experience with air-gapped mainframes aligns with Apollo/Gotham deployments.
  \item \textbf{Location Conflict}: NOTED: Candidate is relocation-ready to within the required 60-minute radius.
\end{itemize}

% ---------------------------------------------------------
\section*{5. Priority Emphasis Areas}

\begin{itemize}[leftmargin=0.2in, label=--]

  \item Emphasize 'Accountability Auditing' to mitigate anti-corporate history.

  \item Leverage 'Adversary Logic' as a unique selling point for Red-Teaming.

  \item Highlight Type 1 Cryptography expertise as a direct match for UKNDS requirements.

\end{itemize}

\vfill
\begin{center}
\textit{This assessment is based on the provided Job Description and the baseline resume as of Monday, February 16, 2026.}
\end{center}

\end{document}